A comparison of different methods for calculating tangent-stiffness matrices in a massively parallel computational peridynamics code.

### 2014-03-28 jacobian_calc_CMAME.tex
Fixed a few build errors

%% if you use PostScript figures in your article
%% use the graphics package for simple commands
%%\usepackage{graphics}
%% or use the graphicx package for more complicated commands
%%\usepackage{graphicx}
%% or use the epsfig package if you prefer to use the old commands
%% \usepackage{epsfig}
%%\usepackage{color}
%%\usepackage{tkz-base}
\usepackage{pgfplots}
\usepackage{siunitx}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{booktabs}
\usepackage{siunitx}
\usepackage{array}
%% The amssymb package provides various useful mathematical symbols
\usepackage{amssymb}

@@

The aim of this paper is not only to \note[Michael]{re: I.1}\change[Michael]{introduce the new}{study the} complex-step method \change[Michael]{in
the context of}{of} evaluating tangent-stiffness matrices, but to serve as a review
for other differentiation techniques useful for solving non-linear systems with
Newton's method. After presenting background information on the underlying
methods to be discussed, presented in this paper are: In subsection~\ref{subsec:TS} a description of
tangent-stiffness matrices, detailed directions for producing
tangent-stiffness matrices with each of the methods identified above, and a
description and justification of the \note[Michael]{re: I.1}\remove[Michael]{new}complex-step method for calculating
tangent-stiffness matrices, in sub-subsection~\ref{subsubsec:Impl} a description of implementing the complex-step method in
the \emph{Peridigm} software, in section~\ref{JGAM} a description of the quantities-of-interest
used to rank the methods, in section~\ref{sec:Res} a presentation and analysis of the results of the
comparative study, and in section~\ref{sec:Conc} conclusions and thoughts on potential future work.
Finally, in the interest of replicable research, the reader is referred to the
corresponding author's website for \emph{Peridigm} C++ source-code and data
necessary to reproduce the results presented here. Additionally, included on
the website is an example serial C++ library with classes for solving
non-linear systems using the techniques discussed here, as well as two
validation and verification example problems which show how to use the library.
The purpose of the serial C++ library is to demonstrate in a less complex
manner than in the \emph{Peridigm} code how one would use
automatic differentiation or complex-step to better encourage their use and
discussion. \note[Michael]{re: II.5}This open source resource is available at the corresponding author's website: http://idl.utsa.edu/jtfoster/paper-repositories/
or directly at https://github.com/utsa-idl/Complex_Step_Jacobian_Project_Archive.

@@

where "$\mathcal{H}_{\boldsymbol{x}}$ is a spherical neighborhood" with a
radius, centered at the original coordinates of a peridynamic node,
$\boldsymbol{x}$, and \boldsymbol{\underline{T}} is the "force vector state
field". The force vector state field maps vectors in the original coordinate system 
measured from the peridynamic node at the center of the neighborhood or 'horizon' to
neighboring peridynamic nodes that fall within the radius of the horizon. $\boldsymbol{b}$ denotes a body force density. Equation~\ref{eqn:PDMotion} may be simplified based on the assumption that
\boldsymbol{\underline{T}} is Riemann integrable and that integral is uniformly
convergent \cite{silling:psa} as,

>>>>

%% if you use PostScript figures in your article
%% use the graphics package for simple commands
%%\usepackage{graphics}
%% or use the graphicx package for more complicated commands
%%\usepackage{graphicx}
%% or use the epsfig package if you prefer to use the old commands
%% \usepackage{epsfig}
%%\usepackage{color}
%%\usepackage{tkz-base}
\usepackage{pgfplots}
\usepackage{siunitx}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{booktabs}
\usepackage{siunitx}
\usepackage{array}
\usepackage{hyperref}
%% The amssymb package provides various useful mathematical symbols
\usepackage{amssymb}

@@

The aim of this paper is not only to \note[Michael]{re: I.1}\change[Michael]{introduce the new}{study the} complex-step method \change[Michael]{in
the context of}{of} evaluating tangent-stiffness matrices, but to serve as a review
for other differentiation techniques useful for solving non-linear systems with
Newton's method. After presenting background information on the underlying
methods to be discussed, presented in this paper are: In subsection~\ref{subsec:TS} a description of
tangent-stiffness matrices, detailed directions for producing
tangent-stiffness matrices with each of the methods identified above, and a
description and justification of the \note[Michael]{re: I.1}\remove[Michael]{new}complex-step method for calculating
tangent-stiffness matrices, in sub-subsection~\ref{subsubsec:Impl} a description of implementing the complex-step method in
the \emph{Peridigm} software, in section~\ref{JGAM} a description of the quantities-of-interest
used to rank the methods, in section~\ref{sec:Res} a presentation and analysis of the results of the
comparative study, and in section~\ref{sec:Conc} conclusions and thoughts on potential future work.
Finally, in the interest of replicable research, the reader is referred to the
corresponding author's website for \emph{Peridigm} C++ source-code and data
necessary to reproduce the results presented here. Additionally, included on
the website is an example serial C++ library with classes for solving
non-linear systems using the techniques discussed here, as well as two
validation and verification example problems which show how to use the library.
The purpose of the serial C++ library is to demonstrate in a less complex
manner than in the \emph{Peridigm} code how one would use
automatic differentiation or complex-step to better encourage their use and
discussion. \note[Michael]{re: II.5}This open source resource is available at the corresponding author's website or at \href{https://github.com/utsa-idl/Complex_Step_Jacobian_Project_Archive}{https://github.com/utsa-idl/Complex\_Step\_Jacobian\_Project\_Archive}.

@@

where "$\mathcal{H}_{\boldsymbol{x}}$ is a spherical neighborhood" with a
radius, centered at the original coordinates of a peridynamic node,
$\boldsymbol{x}$, and $\boldsymbol{\underline{T}}$ is the "force vector state
field". The force vector state field maps vectors in the original coordinate system 
measured from the peridynamic node at the center of the neighborhood or 'horizon' to
neighboring peridynamic nodes that fall within the radius of the horizon. $\boldsymbol{b}$ denotes a body force density. Equation~\ref{eqn:PDMotion} may be simplified based on the assumption that
$\boldsymbol{\underline{T}}$ is Riemann integrable and that integral is uniformly
convergent \cite{silling:psa} as,
